Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-08 paper/paper 2/paper 2.tex
3.3 complexity

As there is no do-it-all language meeting the majority of requirements to formulate constraints, and to validate RDF data,

%which can be used to express constraints and to validate RDF data, 
%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
language selection heavily depends on the individual use case.  Loosely speaking, there are more than 10 candidate languages with different syntaxes and semantics, and we will focus on five which, in our opinion, are the most promising languages on being the standard constraint languages. Those are
\emph{Description Set Profiles (DSP)},
\emph{Resource Shapes (ReSh)}, 
\emph{Shape Expressions (ShEx)},
the \emph{SPARQL Inferencing Notation (SPIN)}, 
and the \emph{Web Ontology Language (OWL 2)}.
%\section{Ideas}
%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language
%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery
The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints and to validate RDF data) in a generic way using a lightweight vocabulary, say,  consisting of only a few terms (see section \ref{sec:vocabulary}).

@@

As there is no standard way to formulate constraints, 
semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint in another other constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
since constraint transformations avoid the necessity to understand several constraint languages.

We provide a validation environment \footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages 
i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.

@@

\tb{use NO bold}

>>>>

As there is no do-it-all language meeting the majority of requirements to formulate constraints and to validate RDF data,
%which can be used to express constraints and to validate RDF data, 
%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
language selection heavily depends on the individual use case.  
There are more than 10 candidate languages with different syntaxes and semantics, and we will focus on five which, in our opinion, are the most promising languages on being the standard constraint languages. Those are
\emph{Description Set Profiles (DSP)},
\emph{Resource Shapes (ReSh)}, 
\emph{Shape Expressions (ShEx)},
the \emph{SPARQL Inferencing Notation (SPIN)}, 
and the \emph{Web Ontology Language (OWL 2)}.
%\section{Ideas}
%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language
%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery
The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints on and to validate RDF data) in a generic way using a lightweight vocabulary which consists of only a few terms (see Section \ref{sec:vocabulary}).

@@

As there is no standard way to formulate constraints, 
semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
since constraint transformations avoid the necessity to understand several constraint languages.

We provide a validation environment\footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, 
i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.

@@
